---
title: "Analyzing cricket players and cricket teams with cricpy template"
author: "Tinniam V Ganesh"
date: "Dec 16, 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

#Introduction
This post shows how you can analyze batsmen, bowlers see [Introducing cricpy:A python package to analyze performances of cricketers](https://gigadom.in/2018/10/28/introducing-cricpya-python-package-to-analyze-performances-of-cricketrs/) and cricket teams see [Cricpy adds team analytics to its arsenal!!] (https://gigadom.in/2019/06/21/cricpy-adds-team-analytics-to-its-repertoire/) in Test, ODI and T20s using cricpy templates, with data from ESPN Cricinfo.

#The **cricpy** package
##A. Analyzing batsmen and bowlers in Test, ODI and T20s
The data for a particular player can be obtained with the getPlayerData() function. To do you will need to go to [ESPN CricInfo Player](http://www.espncricinfo.com/ci/content/player/index.html) and type in the name of the player for e.g Rahul Dravid, Virat Kohli, Alastair Cook etc. This will bring up a page which have the profile number for the player e.g. for Rahul Dravid this would be http://www.espncricinfo.com/india/content/player/28114.html. Hence, Dravid's profile is 28114. This can be used to get the data for Rahul Dravid as shown below

- For Test players use [batting][http://stats.espncricinfo.com/ci/content/records/223646.html] and [bowling](http://stats.espncricinfo.com/ci/content/records/93276.html).
- For ODI use [batting](http://stats.espncricinfo.com/ci/content/records/83548.html) and [bowling](http://stats.espncricinfo.com/ci/content/records/283193.html)
- For T20 use [T20 Batting](http://stats.espncricinfo.com/wi/content/records/283194.html) [T20 Bowling](http://stats.espncricinfo.com/wi/content/records/283194.html)

and select the player you want 
Please mindful of the [ESPN Cricinfo Terms of Use](http://www.espncricinfo.com/ci/content/site/company/terms_use.html) 

My posts on Cripy were

1. [Introducing cricpy:A python package to analyze performances of cricketers](https://gigadom.in/2018/10/28/introducing-cricpya-python-package-to-analyze-performances-of-cricketrs/)
2. [Cricpy takes a swing at the ODIs](https://gigadom.in/2018/11/11/cricpy-takes-a-swing-at-the-odis/)
3. [Cricpy takes guard for the Twenty20s](https://gigadom.in/2018/12/08/cricpy-takes-guard-for-the-twenty20s/)

You can clone/download this cricpy template for your own analysis of players. This can be done using RStudio or IPython notebooks


The cricpy package is now available with  **pip install cricpy!!!** 

##1 Importing cricpy - Python
```{python}
# Install the package
# Do a pip install cricpy
# Import cricpy
import cricpy.analytics as ca 
```


##2. Invoking functions with Python package **cricpy**
```{python}
import cricpy.analytics as ca 
#ca.batsman4s("aplayer.csv","A Player")
```



#3. Getting help from cricpy - Python
```{python}
#help(ca.getPlayerData)
```


The details below will introduce the different functions that are available 
in cricpy.

##4. Get the player data for a player using the function getPlayerData()
**Important Note**
This needs to be done only once for a player. This function stores the player's data in the specified CSV file (for e.g. dravid.csv as above) which can then be reused for all other functions). Once we have the data for the players many analyses can be done. This post will use the stored CSV file obtained with a prior getPlayerData for all subsequent analyses

##4a. For Test players 
```{python}
import cricpy.analytics as ca
#player1 =ca.getPlayerData(profileNo1,dir="..",file="player1.csv",type="batting",homeOrAway=[1,2], result=[1,2,4])
#player1 =ca.getPlayerData(profileNo2,dir="..",file="player2.csv",type="batting",homeOrAway=[1,2], result=[1,2,4])

```

##4b. For ODI players
```{python}
import cricpy.analytics as ca
#player1 =ca.getPlayerDataOD(profileNo1,dir="..",file="player1.csv",type="batting")
#player1 =ca.getPlayerDataOD(profileNo2,dir="..",file="player2.csv",type="batting"")
```


##4c For T20 players
```{python}
import cricpy.analytics as ca
#player1 =ca.getPlayerDataTT(profileNo1,dir="..",file="player1.csv",type="batting")
#player1 =ca.getPlayerDataTT(profileNo2,dir="..",file="player2.csv",type="batting"")
```


##5 A Player's performance -  Basic Analyses
The 3 plots below provide the following for Rahul Dravid

1. Frequency percentage of runs in each run range over the whole career
2. Mean Strike Rate for runs scored in the given range
3. A histogram of runs frequency percentages in runs ranges

```{python basic,cache=TRUE}

import cricpy.analytics as ca
import matplotlib.pyplot as plt


#ca.batsmanRunsFreqPerf("aplayer.csv","A Player")
#ca.batsmanMeanStrikeRate("aplayer.csv","A Player")
#ca.batsmanRunsRanges("aplayer.csv","A Player") 

```

##6. More analyses
This gives details on the batsmen's 4s, 6s and dismissals
```{python dravid-4s6sout,cache=TRUE}
import cricpy.analytics as ca

#ca.batsman4s("aplayer.csv","A Player")
#ca.batsman6s("aplayer.csv","A Player") 
#ca.batsmanDismissals("aplayer.csv","A Player")

# The below function is for ODI and T20 only
#ca.batsmanScoringRateODTT("./kohli.csv","Virat Kohli")  

```

##7.  3D scatter plot and prediction plane
The plots below show the 3D scatter plot of Runs versus Balls Faced and Minutes at crease. A linear regression plane  is then fitted between Runs and Balls Faced + Minutes at crease

```{python dravid-3d,cache=TRUE}
import cricpy.analytics as ca
#ca.battingPerf3d("aplayer.csv","A Player")

```

##8. Average runs at different venues
The plot below gives the average runs scored  at different grounds. The plot also the number of innings at each ground as a label at x-axis. 

```{python dravid-runsgrd,,cache=TRUE}
import cricpy.analytics as ca
#ca.batsmanAvgRunsGround("aplayer.csv","A Player")
```

##9. Average runs against different opposing teams
This plot computes the average runs scored  against different countries. 

```{python dravid-avgopn,,cache=TRUE}
import cricpy.analytics as ca

#ca.batsmanAvgRunsOpposition("aplayer.csv","A Player")
```


##10. Highest Runs Likelihood
The plot below shows the Runs Likelihood for a batsman. 
```{python dravid-kmeans,,cache=TRUE}
import cricpy.analytics as ca

#ca.batsmanRunsLikelihood("aplayer.csv","A Player")
```

#11. A look at the Top 4 batsman 
Choose any number of  players

1.Player1 
2.Player2
3.Player3
...


The following plots take a closer at their performances. The box plots show the median
the 1st and 3rd quartile of the runs

##12. Box Histogram Plot
This plot shows a combined boxplot of the Runs ranges  and a histogram of the Runs Frequency
```{python dakl-boxhist,cache=TRUE}
import cricpy.analytics as ca

#ca.batsmanPerfBoxHist("aplayer001.csv","A Player001")
#ca.batsmanPerfBoxHist("aplayer002.csv","A Player002")
#ca.batsmanPerfBoxHist("aplayer003.csv","A Player003")
#ca.batsmanPerfBoxHist("aplayer004.csv","A Player004")

```

##13. get Player Data special

```{python}
import cricpy.analytics as ca

#player1sp = ca.getPlayerDataSp(profile1,tdir=".",tfile="player1sp.csv",ttype="batting")
#player2sp = ca.getPlayerDataSp(profile2,tdir=".",tfile="player2sp.csv",ttype="batting")
#player3sp = ca.getPlayerDataSp(profile3,tdir=".",tfile="player3sp.csv",ttype="batting")
#player4sp = ca.getPlayerDataSp(profile4,tdir=".",tfile="player4sp.csv",ttype="batting")
```

##14. Contribution to won and lost matches
*Note*:This can only be used for Test matches
```{python ralk-wonlost,cache=TRUE}
import cricpy.analytics as ca

#ca.batsmanContributionWonLost("player1sp.csv","A Player001")
#ca.batsmanContributionWonLost("player2sp.csv","A Player002")
#ca.batsmanContributionWonLost("player3sp.csv","A Player003")
#ca.batsmanContributionWonLost("player4sp.csv","A Player004")

```

##15. Performance at home and overseas
*Note*:This can only be used for Test matches
This function also requires the use of getPlayerDataSp() as shown above
```{python ralk-homeaway,cache=TRUE}
import cricpy.analytics as ca
#ca.batsmanPerfHomeAway("player1sp.csv","A Player001")
#ca.batsmanPerfHomeAway("player2sp.csv","A Player002")
#ca.batsmanPerfHomeAway("player3sp.csv","A Player003")
#ca.batsmanPerfHomeAway("player4sp.csv","A Player004")

```

##16 Moving Average of runs in career

```{python rakl-ma,,cache=TRUE}
import cricpy.analytics as ca

#ca.batsmanMovingAverage("aplayer001.csv","A Player001")
#ca.batsmanMovingAverage("aplayer002.csv","A Player002")
#ca.batsmanMovingAverage("aplayer003.csv","A Player003")
#ca.batsmanMovingAverage("aplayer004.csv","A Player004")

```

##17 Cumulative Average runs of batsman in career
This function provides the cumulative average runs of the batsman over the career. 
```{python rakl-car,,cache=TRUE}
import cricpy.analytics as ca

#ca.batsmanCumulativeAverageRuns("aplayer001.csv","A Player001")
#ca.batsmanCumulativeAverageRuns("aplayer002.csv","A Player002")
#ca.batsmanCumulativeAverageRuns("aplayer003.csv","A Player003")
#ca.batsmanCumulativeAverageRuns("aplayer004.csv","A Player004")

```

##18 Cumulative Average strike rate  of batsman in career
.
```{python rakl-casr,,cache=TRUE}
import cricpy.analytics as ca
#ca.batsmanCumulativeStrikeRate("aplayer001.csv","A Player001")
#ca.batsmanCumulativeStrikeRate("aplayer002.csv","A Player002")
#ca.batsmanCumulativeStrikeRate("aplayer003.csv","A Player003")
#ca.batsmanCumulativeStrikeRate("aplayer004.csv","A Player004")
```

##19 Future Runs forecast 
```{python perffcst,cache-TRUE}
import cricpy.analytics as ca

#ca.batsmanPerfForecast("aplayer001.csv","A Player001")
```

##20 Relative Batsman Cumulative Average Runs
The plot below compares the Relative cumulative average runs of the batsman for each of the runs ranges of 10 and plots them. 

```{python rakl-relSR,cache=TRUE}
import cricpy.analytics as ca

frames = ["aplayer1.csv","aplayer2.csv","aplayer3.csv","aplayer4.csv"]
names = ["A Player1","A Player2","A Player3","A Player4"]
#ca.relativeBatsmanCumulativeAvgRuns(frames,names)

```

##21 Plot of 4s and 6s
```{python kjgs-4s6s, cache=TRUE}
import cricpy.analytics as ca

frames = ["aplayer1.csv","aplayer2.csv","aplayer3.csv","aplayer4.csv"]
names = ["A Player1","A Player2","A Player3","A Player4"]
#ca.batsman4s6s(frames,names)

```

##22. Relative Batsman Strike Rate
The plot below gives the relative Runs Frequency Percetages for each 10 run bucket. The plot below show


```{python rakl-relRunFreq,cache=TRUE}
import cricpy.analytics as ca

frames = ["aplayer1.csv","aplayer2.csv","aplayer3.csv","aplayer4.csv"]
names = ["A Player1","A Player2","A Player3","A Player4"]
#ca.relativeBatsmanCumulativeStrikeRate(frames,names)



```


##23. 3D plot of Runs vs Balls Faced and Minutes at Crease
The plot is a scatter plot of Runs vs Balls faced and Minutes at Crease. A prediction plane is fitted

```{python plot-3,cache=TRUE}
import cricpy.analytics as ca
#ca.battingPerf3d("aplayer001.csv","A Player001")
#ca.battingPerf3d("aplayer002.csv","A Player002")
#ca.battingPerf3d("aplayer003.csv","A Player003")
#ca.battingPerf3d("aplayer004.csv","A Player004")
```



##24. Predicting Runs given Balls Faced and Minutes at Crease
A multi-variate regression plane is fitted between Runs and Balls faced +Minutes at crease.
```{python messages=FALSE,cache=TRUE}
import cricpy.analytics as ca

import numpy as np
import pandas as pd

BF = np.linspace( 10, 400,15)
Mins = np.linspace( 30,600,15)
newDF= pd.DataFrame({'BF':BF,'Mins':Mins})

#aplayer = ca.batsmanRunsPredict("aplayer.csv",newDF,"A Player")
#print(aplayer)

```

The fitted model is then used to predict the runs that the batsmen will score for a given Balls faced and Minutes at crease. 

##25 Analysis of Top 3 wicket takers
Take any number of bowlers from either Test, ODI or T20

1. Bowler1
2. Bowler2
3. Bowler3
...


##26. Get the bowler's data (Test)
This plot below computes the percentage frequency of number of wickets taken for e.g
1 wicket x%, 2 wickets y% etc and plots them as a continuous line 

```{python}
import cricpy.analytics as ca

#abowler1 =ca.getPlayerData(profileNo1,dir=".",file="abowler1.csv",type="bowling",homeOrAway=[1,2], result=[1,2,4])
#abowler2 =ca.getPlayerData(profileNo2,dir=".",file="abowler2.csv",type="bowling",homeOrAway=[1,2], result=[1,2,4])
#abowler3 =ca.getPlayerData(profile3,dir=".",file="abowler3.csv",type="bowling",homeOrAway=[1,2], result=[1,2,4])
```


##26b For ODI bowlers
```{python}
import cricpy.analytics as ca

#abowler1 =ca.getPlayerDataOD(profileNo1,dir=".",file="abowler1.csv",type="bowling")
#abowler2 =ca.getPlayerDataOD(profileNo2,dir=".",file="abowler2.csv",type="bowling")
#abowler3 =ca.getPlayerDataOD(profile3,dir=".",file="abowler3.csv",type="bowling")
```

## 26c For T20 bowlers
```{python}
import cricpy.analytics as ca

#abowler1 =ca.getPlayerDataTT(profileNo1,dir=".",file="abowler1.csv",type="bowling")
#abowler2 =ca.getPlayerDataTT(profileNo2,dir=".",file="abowler2.csv",type="bowling")
#abowler3 =ca.getPlayerDataTT(profile3,dir=".",file="abowler3.csv",type="bowling")
```

##27. Wicket Frequency Plot
This plot below plots the frequency of wickets taken for each of the bowlers

```{python relBowlFP,,cache=TRUE}
import cricpy.analytics as ca

#ca.bowlerWktsFreqPercent("abowler1.csv","A Bowler1")
#ca.bowlerWktsFreqPercent("abowler2.csv","A Bowler2")
#ca.bowlerWktsFreqPercent("abowler3.csv","A Bowler3")

```

##28. Wickets Runs plot
The plot below create a box plot showing the 1st and 3rd quartile of runs conceded versus the number of wickets taken

```{python wktsrun,cache =TRUE}
import cricpy.analytics as ca

#ca.bowlerWktsRunsPlot("abowler1.csv","A Bowler1")
#ca.bowlerWktsRunsPlot("abowler2.csv","A Bowler2")
#ca.bowlerWktsRunsPlot("abowler3.csv","A Bowler3")

```

##29 Average wickets at different venues
The plot gives the average wickets taken bat different venues. 

```{python avgWktshrg,,cache=TRUE}
import cricpy.analytics as ca

#ca.bowlerAvgWktsGround("abowler1.csv","A Bowler1")
#ca.bowlerAvgWktsGround("abowler2.csv","A Bowler2")
#ca.bowlerAvgWktsGround("abowler3.csv","A Bowler3")


```

##30 Average wickets against different opposition
The plot gives the average wickets taken against different countries.

```{python avgWktoppn,cache=TRUE}
import cricpy.analytics as ca

#ca.bowlerAvgWktsOpposition("abowler1.csv","A Bowler1")
#ca.bowlerAvgWktsOpposition("abowler2.csv","A Bowler2")
#ca.bowlerAvgWktsOpposition("abowler3.csv","A Bowler3")

```


##31 Wickets taken moving average

```{python mka-bowlma,,cache=TRUE}
import cricpy.analytics as ca

#ca.bowlerMovingAverage("abowler1.csv","A Bowler1")
#ca.bowlerMovingAverage("abowler2.csv","A Bowler2")
#ca.bowlerMovingAverage("abowler3.csv","A Bowler3")

```

##32 Cumulative average wickets taken
The plots below give the cumulative average wickets taken by the bowlers.
```{python mka-bowlcaw,,cache=TRUE}
import cricpy.analytics as ca

#ca.bowlerCumulativeAvgWickets("abowler1.csv","A Bowler1")
#ca.bowlerCumulativeAvgWickets("abowler2.csv","A Bowler2")
#ca.bowlerCumulativeAvgWickets("abowler3.csv","A Bowler3")

```

##33 Cumulative average economy rate
The plots below give the cumulative average economy rate of the bowlers. 
```{python mka-bowler,,cache=TRUE}
import cricpy.analytics as ca

#ca.bowlerCumulativeAvgEconRate("abowler1.csv","A Bowler1")
#ca.bowlerCumulativeAvgEconRate("abowler2.csv","A Bowler2")
#ca.bowlerCumulativeAvgEconRate("abowler3.csv","A Bowler3")

```

##34 Future Wickets forecast 

```{python mka-perffcst,,cache=TRUE}
import cricpy.analytics as ca
#ca.bowlerPerfForecast("abowler1.csv","A bowler1")
```

##35 Get player data special


```{python}
import cricpy.analytics as ca

#abowler1sp =ca.getPlayerDataSp(profile1,tdir=".",tfile="abowler1sp.csv",ttype="bowling")
#abowler2sp =ca.getPlayerDataSp(profile2,tdir=".",tfile="abowler2sp.csv",ttype="bowling")
#abowler3sp =ca.getPlayerDataSp(profile3,tdir=".",tfile="abowler3sp.csv",ttype="bowling")
```



##36 Contribution to matches won and lost
*Note*:This can be done only for Test cricketers


```{python mka-wl,cache=TRUE}
import cricpy.analytics as ca

#ca.bowlerContributionWonLost("abowler1sp.csv","A Bowler1")
#ca.bowlerContributionWonLost("abowler2sp.csv","A Bowler2")
#ca.bowlerContributionWonLost("abowler3sp.csv","A Bowler3")


```

##37 Performance home and overseas
*Note*:This can be done only for Test cricketers

```{python mka-ha,cache=TRUE}
import cricpy.analytics as ca

#ca.bowlerPerfHomeAway("abowler1sp.csv","A Bowler1")
#ca.bowlerPerfHomeAway("abowler2sp.csv","A Bowler2")
#ca.bowlerPerfHomeAway("abowler3sp.csv","A Bowler3")

```

##38 Relative cumulative average economy rate of bowlers

```{python relBowlPerf,cache=TRUE}
import cricpy.analytics as ca

frames = ["abowler1.csv","abowler2.csv","abowler3.csv"]
names = ["A Bowler1","A Bowler2","A Bowler3"]
#ca.relativeBowlerCumulativeAvgEconRate(frames,names)
```

##39 Relative Economy Rate against wickets taken

```{python relBowlER,cache=TRUE}
import cricpy.analytics as ca

frames = ["abowler1.csv","abowler2.csv","abowler3.csv"]
names = ["A Bowler1","A Bowler2","A Bowler3"]
#ca.relativeBowlingER(frames,names)

```

##40 Relative cumulative average wickets of bowlers in career

```{python rbcaw,cache=TRUE}
import cricpy.analytics as ca
frames = ["abowler1.csv","abowler2.csv","abowler3.csv"]
names = ["A Bowler1","A Bowler2","A Bowler3"]
#ca.relativeBowlerCumulativeAvgWickets(frames,names)

```

##B. Analyzing cricket teams in Test, ODI and T20s

The following functions will get the team data for Tests, ODI and T20s

###1a. Get Test team data
```{r}
#country1Test= getTeamDataHomeAway(dir=".",teamView="bat",matchType="Test",file="country1Test.csv",save=True,teamName="Country1")
#country2Test= getTeamDataHomeAway(dir=".",teamView="bat",matchType="Test",file="country2Test.csv",save=True,teamName="Country2")
#country3Test= getTeamDataHomeAway(dir=".",teamView="bat",matchType="Test",file="country3Test.csv",save=True,teamName="Country3")
```

###1b. Get ODI team  data
```{r}
#team1ODI=  getTeamDataHomeAway(dir=".",matchType="ODI",file="team1ODI.csv",save=True,teamName="team1")
#team2ODI=  getTeamDataHomeAway(dir=".",matchType="ODI",file="team2ODI.csv",save=True,teamName="team2")
#team3ODI=  getTeamDataHomeAway(dir=".",matchType="ODI",file="team3ODI.csv",save=True,teamName="team3")
```

###1c. Get T20 team  data
```{r}
#team1T20 = getTeamDataHomeAway(matchType="T20",file="team1T20.csv",save=True,teamName="team1")
#team2T20 = getTeamDataHomeAway(matchType="T20",file="team2T20.csv",save=True,teamName="team2")
#team3T20 = getTeamDataHomeAway(matchType="T20",file="team3T20.csv",save=True,teamName="team3")
```

###2a. Test - Analyzing test performances against opposition
```{r}
# Get the performance of Indian test team against all teams at all venues as a dataframe
#df = teamWinLossStatusVsOpposition("country1Test.csv",teamName="Country1",opposition=["all"],homeOrAway=["all"],matchType="Test",plot=False)
print(df.head())
# Plot the performance of Country1 Test team  against all teams at all venues
#teamWinLossStatusVsOpposition("country1Test.csv",teamName="Country1",opposition=["all"],homeOrAway=["all"],matchType="Test",plot=True)
# Plot the performance of Country1 Test team  against specific teams at home/away venues
#teamWinLossStatusVsOpposition("country1Test.csv",teamName="Country1",opposition=["Country2","Country3","Country4"],homeOrAway=["home","away","neutral"],matchType="Test",plot=True)
```


###2b. Test - Analyzing test performances against opposition at different grounds
```{r}
# Get the performance of Indian test team against all teams at all venues as a dataframe
#df = teamWinLossStatusAtGrounds("country1Test.csv",teamName="Country1",opposition=["all"],homeOrAway=["all"],matchType="Test",plot=False)
#df.head()
# Plot the performance of Country1 Test team  against all teams at all venues
#teamWinLossStatusAtGrounds("country1Test.csv",teamName="Country1",opposition=["all"],homeOrAway=["all"],matchType="Test",plot=True)
# Plot the performance of Country1 Test team  against specific teams at home/away venues
#teamWinLossStatusAtGrounds("country1Test.csv",teamName="Country1",opposition=["Country2","Country3","Country4"],homeOrAway=["home","away","neutral"],matchType="Test",plot=True)
```

###2c. Test - Plot time lines of wins and losses
```{r}
#plotTimelineofWinsLosses("country1Test.csv",team="Country1",opposition=["all"], #startDate="1970-01-01",endDate="2017-01-01")
#plotTimelineofWinsLosses("country1Test.csv",team="Country1",opposition=["Country2","Count#ry3","Country4"], homeOrAway=["home",away","neutral"], startDate=<start Date> #,endDate=<endDate>)
```

###3a. ODI - Analyzing test performances against opposition
```{r}
#df = teamWinLossStatusVsOpposition("team1ODI.csv",teamName="Team1",opposition=["all"],homeOrAway=["all"],matchType="ODI",plot=False)
#print(df.head())
# Plot the performance of team1  in ODIs against Sri Lanka, India at all venues
#teamWinLossStatusVsOpposition("team1ODI.csv",teamName="Team1",opposition=["all"],homeOrAway=[all"],matchType="ODI",plot=True)
# Plot the performance of Team1 ODI team  against specific teams at home/away venues
#teamWinLossStatusVsOpposition("team1ODI.csv",teamName="Team1",opposition=["Team2","Team3","Team4"],homeOrAway="home","away","neutral"],matchType="ODI",plot=True)
```

###3b. ODI - Analyzing test performances against opposition at different venues
```{r}
#df = teamWinLossStatusAtGrounds("team1ODI.csv",teamName="Team1",opposition=["all"],homeOrAway=["all"],matchType="ODI",plot=False)
#print(df.head())
# Plot the performance of Team1s in ODIs specific ODI teams at all venues
#teamWinLossStatusAtGrounds("team1ODI.csv",teamName="Team1",opposition=["all"],homeOrAway=[all"],matchType="ODI",plot=True)
# Plot the performance of Team1 against specific ODI teams at home/away venues
#teamWinLossStatusAtGrounds("team1ODI.csv",teamName="Team1",opposition=["Team2","Team3","Team4"],homeOrAway=["home","away","neutral"],matchType="ODI",plot=True)
```


###3c. ODI - Plot time lines of wins and losses
```{r}
#Plot the time line of wins/losses of Bangladesh ODI team between 2 dates all venues
#plotTimelineofWinsLosses("team1ODI.csv",team="Team1",startDate=<start date> ,endDa#te=<end date>,matchType="ODI")
#Plot the time line of wins/losses against specific opposition between 2 dates
#plotTimelineofWinsLosses("team1ODI.csv",team="Team1",opposition=["Team2","Team2"], homeOrAway=["home",away","neutral"], startDate=<start date>,endDate=<end date> ,matchType="ODI")
```


###4a. T20 - Analyzing test performances against opposition
```{r}
#df = teamWinLossStatusVsOpposition("teamT20.csv",teamName="Team1",opposition=["all"],homeOrAway=["all"],matchType="T20",plot=False)
#print(df.head())
# Plot the performance of Team1 in T20s  against  all opposition at all venues
#teamWinLossStatusVsOpposition("teamT20.csv",teamName="Team1",opposition=["all"],homeOrAway=[all"],matchType="T20",plot=True)
# Plot the performance of T20 Test team  against specific teams at home/away venues
#teamWinLossStatusVsOpposition("teamT20.csv",teamName="Team1",opposition=["Team2","Team3","Team4"],homeOrAway=["home","away","neutral"],matchType="T20",plot=True)
```

###4b. T20 - Analyzing test performances against opposition at different venues
```{r}
#df = teamWinLossStatusAtGrounds("teamT20.csv",teamName="Team1",opposition=["all"],homeOrAway=["all"],matchType="T20",plot=False)
#df.head()
# Plot the performance of Team1s in ODIs specific ODI teams at all venues
#teamWinLossStatusAtGrounds("teamT20.csv",teamName="Team1",opposition=["all"],homeOrAway=["all"],matchType="T20",plot=True)
# Plot the performance of Team1 against specific ODI teams at home/away venues
#teamWinLossStatusAtGrounds("teamT20.csv",teamName="Team1",opposition=["Team2","Team3","Team4"],homeOrAway=["home","away","neutral"],matchType="T20",plot=True)
```


###4c. T20 - Plot time lines of wins and losses
```{r}
#Plot the time line of wins/losses of Bangladesh ODI team between 2 dates all venues
#plotTimelineofWinsLosses("teamT20.csv",team="Team1",startDate=<start date> ,endDa#te=<end date>,matchType="T20")
#Plot the time line of wins/losses against specific opposition between 2 dates
#plotTimelineofWinsLosses("teamT20.csv",team="Team1",opposition=c("Team2","Team2"), homeOrAway=c("home",away","neutral"), startDate=<start date>,endDate=<end date> ,matchType="T20")
```

## Conclusion

# Key Findings


## Analysis of batsman


##Analysis of bowlers


## Analysis of teams


